---
output:
  pdf_document:
    number_sections: no
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      cache.lazy = FALSE,
                      # force output to LaTeX (which forces the
                      # imposition of fig.pos) and proper figure alignment
                      fig.align = 'center',
                      fig.pos = 'H')

library(dplyr)
library(here)
library(tidyr)
library(stringr)
library(forcats)
library(broom)
library(readr)
library(jsonlite)

library(kableExtra)

library(gridExtra)

library(ggplot2)
# needs to be run only once
# extrafont::font_import()
extrafont::loadfonts(quiet = TRUE)
# devtools::install_github("hrbrmstr/hrbrthemes")
library(GGally)
library(hrbrthemes)
theme_set(theme_ipsum())
library(atheylab.utils)

knitr::knit_hooks$set(inline = function(x) {
  atheylab.utils::pretty_print_inline(x, decimals = 2)
})

library(texreg)

```

---
title: "MS&E 234 Project"
---

```{r}
################################################################################
# data import + tidying
################################################################################

# raw video info
read_csv(here::here('derived_data/video_info.csv'), na = c("", -1)) %>%
  mutate_at(vars(category, dislikes, likes, views, n_comments), as.integer) -> raw

# category id <-> category name crosswalk
category_crosswalk <- read_csv(here::here('derived_data/category_crosswalk.csv'))

# search info dataframe
read_csv(here::here('derived_data/search_info.csv'), na = c("", -1)) %>%
  select(-recommendations) %>%
  mutate(search = stringr::str_replace_all(search, ' ', '_')) -> search_info

# description sentiment 
read_csv(here::here('derived_data/description_sentiments.csv')) %>%
  rename(description_polarity = polarity) -> sentiment_descriptions

# comment sentiment
read_csv(here::here('derived_data/comment_sentiments.csv')) %>%
  rename(comment_polarity = polarity) -> sentiment_comments

# captions sentiment
read_csv(here::here('derived_data/caption_sentiments.csv')) %>%
  rename(caption_polarity = polarity) -> sentiment_captions

raw %>%
  left_join(sentiment_descriptions, by = 'video_id') %>%
  left_join(sentiment_comments, by = 'video_id') %>%
  left_join(sentiment_captions, by = 'video_id') -> video_info

# add a variable for percent of likes
video_info %>%
  mutate(p_like = likes / (likes + dislikes)) -> video_info

# video degrees
degrees <- read_csv(here::here('derived_data/vertex_degrees.csv'))
  
```

Basic summaries across all our variables:

```{r}
search_info %>%
  left_join(video_info, by = 'video_id') -> search_w_info

search_w_info %>%
  rename_all(list(~ stringr::str_replace(., "_", "."))) %>%
  select(views, likes, dislikes, n.comments, description.polarity, comment.polarity, caption.polarity) %>%
  summarise_all(list(min = ~min(., na.rm = TRUE),
                     median = ~median(., na.rm = TRUE),
                     max = ~max(., na.rm = TRUE),
                     mean = ~mean(., na.rm = TRUE),
                     sd = ~sd(., na.rm = TRUE))) -> summary_stats

summary_stats %>%
  gather(stat, val) %>%
  tidyr::separate(stat, into = c("var", "stat"), sep = "_", extra = "merge") %>%
  spread(stat, val) %>%
  select(Variable = var, mean, median, min, max, sd) %>%
  kable(format = "latex",
        caption = "Summaries",
        booktabs = TRUE,
        digits = 2) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))

```


Now asking the question: did any features of our videos change (on average) as we traversed the trees?

```{r}
# get average statistics by search depth
search_w_info %>%
  group_by(depth) %>%
  summarise_at(vars(likes, n_comments, views, description_polarity, comment_polarity, caption_polarity, p_like),
               function(x) mean(x, na.rm = TRUE)) %>%
  gather(stat, mean, -depth) -> mean_by_depth

search_w_info %>%
  group_by(depth) %>%
  summarise_at(vars(likes, n_comments, views, description_polarity, comment_polarity, caption_polarity, p_like),
               function(x) sd(x, na.rm = TRUE) / sqrt(length(x))) %>%
  gather(stat, se, -depth) -> se_by_depth

mean_by_depth %>%
  left_join(se_by_depth, by = c('depth', 'stat')) -> stats_by_depth

stats_by_depth %>%
  ggplot(aes(depth, mean)) +
  geom_line() +
  facet_wrap(~ stat, scales="free_y")

```

This gives us an overview. For the sake of less ugly plots let's make these individually

```{r}
stats_by_depth %>%
  filter(stat == "views") %>%
  ggplot(aes(depth, mean)) +
  geom_line() +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2) +
  ylab("Average Views") +
  xlab("BFS Depth") +
  scale_x_continuous(breaks=1:8)
```


```{r}
stats_by_depth %>%
  filter(stat == "comment_polarity") %>%
  ggplot(aes(depth, mean)) +
  geom_line() +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2) +
  ylab("Average Comment Polarity") +
  xlab("BFS Depth") + 
  scale_x_continuous(breaks=1:8)
```

```{r}
stats_by_depth %>%
  filter(stat == "description_polarity") %>%
  ggplot(aes(depth, mean)) +
  geom_line() +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2) +
  ylab("Average Description Polarity") +
  xlab("BFS Depth") + 
  scale_x_continuous(breaks=1:8)
```


```{r}
stats_by_depth %>%
  filter(stat == "caption_polarity") %>%
  ggplot(aes(depth, mean)) +
  geom_line() +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2) +
  ylab("Average Caption Polarity") +
  xlab("BFS Depth") + 
  scale_x_continuous(breaks=1:8)
```


```{r}
stats_by_depth %>%
  filter(stat == "p_like") %>%
  mutate(mean = 1 - mean,
         stat = "p_dislike") %>%
  select(-se) -> dislikes

stats_by_depth %>%
  bind_rows(dislikes) %>%
  filter(stat %in% c("p_like", "p_dislike")) %>%
  mutate(stat = ifelse(stat == "p_like", "Likes", "Dislikes")) %>%
  ggplot(aes(depth, mean, fill=stat)) +
  geom_area() +
  ylab("Fraction of Likes/Dislikes") +
  xlab("BFS Depth") + 
  scale_fill_manual(name = "", values = c("red", "darkgreen")) +
  scale_x_continuous(breaks=1:8)

```

What happens to our categories as we go _deeperrr_?

```{r}
search_w_info %>%
  left_join(category_crosswalk, by = c('category' = 'category_id')) %>%
  mutate_at("category_name", as.factor) %>%
  group_by(depth, category_name) %>%
  summarise(n = n()) %>%
  mutate(category_freq = n / sum(n)) -> category_freq

category_freq %>%
  group_by(depth) %>%
  summarise(sum = sum(category_freq)) -> tst

category_freq %>%
  ggplot(aes(depth, category_freq, fill = category_name)) + 
  geom_col() +
  xlab("BFS Depth") + 
  ylab("Frequency")

```

# Graphy things

```{r}
# degree distribution
n_videos <- nrow(degrees)

degrees %>%
  group_by(in_deg) %>%
  summarise(p = n() / n_videos) %>%
  ggplot(aes(in_deg, p)) + 
  geom_point() + 
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = scales::trans_format("log10", scales::math_format(10^.x))) + 
  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
                labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  ylab("P(in-degree)") + 
  xlab("in-degree") 
  


```

Look at characteristics by in-degree. First: what did the videos with the highest in-degree look like?

```{r}
degrees %>%
  select(video_id, in_deg) %>%
  top_n(8, in_deg) %>%
  arrange(-in_deg) %>%
  left_join(video_info %>% select(video_id, title, channel, category), by = "video_id") %>%
  left_join(category_crosswalk, by = c('category' = 'category_id')) %>%
  select(-category) %>%
  kable(format = "latex",
        caption = "Top Videos by In-Degree",
        col.names = c("Video", "In-Degree", "Title", "Channel", "Category"),
        booktabs = TRUE,
        digits = 2) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
  
```

